\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-04 lang-design.tex
comment

These two examples both show the incompatibility between exposing the concrete definition of a field for reasoning (this second example even involves the definition of fixpoint and pattern matching) and overridability. We need to be careful about this tension when designing the language.

\textlabel{Challenge (3)}{chg:consistency}~\textbf{Consistency vs. Self Parametrization}. The metatheoretical formulation in~\citet{zm2017} for family polymorphism is very natural as they consider an extension of the family as the concatenation of a new linkage. However, this formulation is not directly adaptable for dependent type theory because it can easily encode non-termination sabotaging consistency by the presence of "self". Informally, in the orignal formulation, we can override the "f" in family $\{"f" := id; "g" := "call self.f"\}$ with "call self.g", resulting the mutual calling of "f" and "g" thus a deadloop. This conflict between self parametrization and consistency requests changing the original formulation of family and inheritance for dependent type theory.

\textlabel{Challenge (4)}{chg:software-engineering}~\textbf{Engineering and Ecosystem}.  Not only for the metatheory, we also want our implementation of family to have good compatibility with the rest of Coq. For example, we shouldn't compromise \textbf{tactic programming} as it is part of the idiomatic Coq programming. Additionally, the interactive development style requires \textbf{incremental type checking}---our design has to be able to type check each Coq Vernacular command once inputted. What's more, we want our family ``term'' to incorporate Coq \textbf{without breaking its other functionality}. For example, the user may want to project the family member anywhere inside an arbitrary Gallina term, that may later be computed and normalized. However, families themselves can be second class citizens just like \citet{zm2017}.\YZ{I was thinking if the paper should start by talking about the functional encoding of inheritance (namely exposing a self parameter to allow late binding, and later taking the fixpoint of the extensible module when it needs to be accessed outside the family).  I think most readers will benefit from a recap of this encoding.\\
Coq is total but that doesn’t prevent Coq from having a Fixpoint keyword (plus you proved your language is consistent).
}

>>>>

These two examples both show the incompatibility between exposing the
concrete definition of a field for reasoning (this second example even
involves the definition of fixpoint and pattern matching) and
overridability. We need to be careful about this tension when designing
the language.\YZ{
  The two examples seem to suggest there should not be any overriding allowed at all.
  Is there an example where you actually want the ability to override?
}

\textlabel{Challenge (3)}{chg:consistency}~\textbf{Consistency vs. Self Parametrization}.
The meta\-theoretical formulation in~\citet{zm2017} for family
polymorphism is very natural as they consider an extension of the family
as the concatenation of a new linkage. However, this formulation is not
directly adaptable for dependent type theory because it can easily
encode non-termination sabotaging consistency by the presence of "self".
Informally, in the orignal formulation, we can override the "f" in
family $\{"f" := id; "g" := "call self.f"\}$ with "call self.g",
resulting the mutual calling of "f" and "g" thus a deadloop. This
conflict between self parametrization and consistency requests changing
the original formulation of family and inheritance for dependent type
theory.

\textlabel{Challenge (4)}{chg:software-engineering}~\textbf{Engineering and Ecosystem}.
Not only for the metatheory, we also want our implementation of family
to have good compatibility with the rest of Coq. For example, we
shouldn't compromise \textbf{tactic programming} as it is part of the
idiomatic Coq programming experience. Additionally, the interactive development
style requires \textbf{incremental type checking}---our design has to be
able to type check each Coq Vernacular command once inputted. What's
more, we want our family ``term'' to be incorporated into Coq \textbf{without
breaking its other functionality}. For example, the user may want to
project the family member anywhere inside an arbitrary Gallina term,
that may later be computed and normalized. However, families themselves
can be second class citizens just like \citet{zm2017}.\YZ{I was thinking
if the paper should start by talking about the functional encoding of
inheritance (namely exposing a self parameter to allow late binding, and
later taking the fixpoint of the extensible module when it needs to be
accessed outside the family).  I think most readers will benefit from a
recap of this encoding.\\
Coq is total but that doesn’t prevent Coq from having a Fixpoint keyword (plus you proved your language is consistent).
}
